Disparity through time - for appendix

### 2017-12-12 analyses/05-figure-dtt.Rmd
Reorder analysis files

# Modify data - add midpoints, remove missing data, filter to just two models,
# make disparity relative by dividing by max values
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

# Modify data - add midpoints, remove missing data, filter to just two models
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

>>>>

# Modify data - add midpoints, remove missing data, filter to just three models,
# make disparity relative by dividing by max values
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

# Modify data - add midpoints, remove missing data, filter to just three models
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

### 2017-12-12 analyses/figure-dtt-appendix.Rmd
Reorder analysis files

---
title: "Disparity through time - simplified and for appendix"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

# Modify data - add midpoints, remove missing data, filter to just three models,
# make disparity relative by dividing by max values
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

duration2 <- 
  duration %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

number2 <- 
  number %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))
```

@@

# Modify data - add midpoints, remove missing data, filter to just three models
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  filter(model == "equalbins" | model == "proximity" | model == "gradual.split") %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

pdf("../manuscript/figures/fig-dtt-age.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

@@

pdf("../manuscript/figures/fig-dtt-epoch.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

>>>>

---
title: "Disparity through time - for appendix"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

# Modify data - add midpoints, remove missing data, filter to just two models,
# make disparity relative by dividing by max values
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%

  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

duration2 <- 
  duration %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%

  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

number2 <- 
  number %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%

  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))
```

@@

# Modify data - add midpoints, remove missing data, filter to just two models
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%

  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

pdf("../manuscript/figures/fig-dtt-age-appendix.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

@@

pdf("../manuscript/figures/fig-dtt-epoch-appendix.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```
